### 2022-07-29 doc/university-covid.tex
sig

@@

>>>>

\usepackage{lineno}
\linenumbers

@@

\section*{Significance}

University campuses present challenges to preventing SARS-CoV-2 transmission due to a high proportion of asymptomatic infections and high contact rates. SARS-CoV-2 outbreaks on the Princeton University campus offer an unusually well-documented perspective, rooted in mass asymptomatic testing, which was further informed by mathematical modeling approaches. Here, we test whether this model, which was previously used for guiding policy decisions, can capture the observed outbreak patterns on campus. Our analysis reveals strong coupling in epidemic dynamics on campus and in local communities.  Super-spreading events can drive transmission on campus, thereby weakening the dynamical coupling in campus and community outbreaks.
